Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-19 paper/paper.tex
write on the median scattering

@@

% TODO declare new math operator
\begin{equation}
\boldsymbol{\mu}(p) =
\mathrm{median}
\int_{\mathbb{R}} \mathbf{S}\boldsymbol{x}_n(t, p) \;\mathrm{d}t
\end{equation}

>>>>

\DeclareMathOperator*{\median}{median}

@@

Given a collection of $N$ such waveforms, we number them arbitrarily from $\boldsymbol{x}_1$ to $\boldsymbol{x}_N$. Then, for every path $p$ in the joint time--frequency scattering transform operator $\mathbf{S}$, we measure the median value taken by the average response of $\mathbf{S}\boldsymbol{x}_n$ across all samples $n$ from $1$ to $N$:
\begin{equation}
\boldsymbol{\mu}(p) =
\median_{1\leq n \leq N}
\int_{\mathbb{R}} \mathbf{S}\boldsymbol{x}_n(t, p) \;\mathrm{d}t.
\end{equation}

\begin{equation}
\mathbf{\widetilde{S}}\boldsymbol{x}_n (p) =
\log \left(
1 +
\dfrac{
\int_\mathbb{R} \mathbf{S}\boldsymbol{x}_n (t, p) \;\mathrm{d}t
}{\varepsilon \times \boldsymbol{\mu}(p)}
\right)
\end{equation}
